3D Magnetic modelling of ellipsoidal bodies

### 2017-02-20 manuscript/manuscript.tex
include the new limit for the isotropic susceptibility

%The angular difference $\theta$ between the resultant magnetization
%and the inducing field is the same, whether the quantities
%are defined in the main coordinate system (Fig. \ref{fig:orientation-angles}a)
%or local coordinate system (Fig. \ref{fig:orientation-angles}b).
%For convenience, we define $\theta$ (in degrees) in the main coordinate system
%by using the scalar product definition as follows:
%\begin{equation}
%\theta = \frac{180}{\pi} \, \cos^{-1} \left( 
%\frac{\mathbf{M}^{\top}\mathbf{H}_{0}}
%{\| \mathbf{M} \| \; \| \mathbf{H}_{0} \|}\right) \: ,
%\label{eq:theta}
%\end{equation}
%where $\mathbf{M}$ is obtained by pre-multiplying the
%magnetization $\tilde{\mathbf{M}}$ (Eq. \ref{eq:M-tilde-remanence})
%by the orthogonal matrix $\mathbf{V}$ (Eq. \ref{eq:A}),
%which is defined according to the ellipsoid type, and
%$\mathbf{H}_{0}$ is given by Eq. \ref{eq:H0}.
%
For the particular case in which the susceptibility is isotropic,
the susceptibility tensor is defined according to Eq. \ref{eq:K-isotropic}.
In this case, the magnetization $\mathbf{M}$ (Eqs. \ref{eq:M-KH} and \ref{eq:M-remanence}),
referred to the main coordinate system (Fig. \ref{fig:orientation-angles}a),
and the matrix $\mathbf{\Lambda}$ (Eq. \ref{eq:Lambda})
can be rewritten as follows:
\begin{equation}
\mathbf{M} = \mathbf{\Lambda} \left( \chi \, \mathbf{H}_{0} +
\mathbf{M}_{R} \right) \: ,
\label{eq:M-K-isotropic}
\end{equation}
and
\begin{equation}
\mathbf{\Lambda} = \mathbf{V}
\left[ \begin{array}{ccc}
\frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{11}} &  &  \\
 & \frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{22}} &  \\
 &  & \frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{33}}
\end{array} \right] \mathbf{V}^{\top} \: .
\label{eq:Lambda-K-isotropic}
\end{equation}
Despite the coordinate transformation represented by
matrix $\mathbf{V}$ (Eq. \ref{eq:A}),
this equation is in perfect agreement with those presented 
by \citet[Eqs. ~13--15]{guo2001}.
The first term, depending on the inducing field $\mathbf{H}_{0}$
(Eq. \ref{eq:H0}), 
represents the induced magnetization whereas the term depending on
$\mathbf{M}_{R}$ is the remanent magnetization.
Equation \ref{eq:M-K-isotropic} reveals that, as pointed out by
many authors
\citep[e.g.,][]{maxwell1873, dubois1896, stoner1945, clark1986, sttraton2007},
the induced magnetization opposes the inducing field 
if it is parallel to an ellipsoid axis, 
independently of the ellipsoid type. Otherwise, the
magnetization is not necessarily parallel to
the inducing field.
If we additionally consider that $\chi << 1$, the matrix 
$\mathbf{\Lambda}$ (Eq. \ref{eq:Lambda-K-isotropic})
approaches to the identity and the magnetization
$\mathbf{M}$ (Eq. \ref{eq:M-K-isotropic})
can be approximated as follows:
\begin{equation}
\mathbf{M} \approx \chi \, \mathbf{H}_{0} +
\mathbf{M}_{R} \: ,
\label{eq:M-approx}
\end{equation}
which is the classical equation describing the resultant
magnetization in applied geophysics \citep[p. ~89]{blakely1996}.
Notice that, in this particular case, the induced magnetization
is parallel to the inducing field $\mathbf{H}_{0}$ (Eq. \ref{eq:H0}),
whether it is parallel to an ellipsoid axis or not.
Usually, Eq. \ref{eq:M-approx}
is considered a good approximation for $\chi \leq 0.1$ SI.

INCLUIR A MEDIDA THETA
\begin{equation}
\theta = \frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{11}} +
\frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{22}} +
\frac{1}{1 - \chi \, \tilde{n}^{\dagger}_{33}} - 3 \: .
\label{eq:theta}
\end{equation}

>>>>

%The angular difference $\theta$ between the resultant magnetization
%and the inducing field is the same, whether the quantities
%are defined in the main coordinate system (Fig. \ref{fig:orientation-angles}a)
%or local coordinate system (Fig. \ref{fig:orientation-angles}b).
%For convenience, we define $\theta$ (in degrees) in the main coordinate system
%by using the scalar product definition as follows:
%\begin{equation}
%\theta = \frac{180}{\pi} \, \cos^{-1} \left( 
%\frac{\mathbf{M}^{\top}\mathbf{H}_{0}}
%{\| \mathbf{M} \| \; \| \mathbf{H}_{0} \|}\right) \: ,
%\label{eq:theta}
%\end{equation}
%where $\mathbf{M}$ is obtained by pre-multiplying the
%magnetization $\tilde{\mathbf{M}}$ (Eq. \ref{eq:M-tilde-remanence})
%by the orthogonal matrix $\mathbf{V}$ (Eq. \ref{eq:A}),
%which is defined according to the ellipsoid type, and
%$\mathbf{H}_{0}$ is given by Eq. \ref{eq:H0}.
%
For the particular case in which the susceptibility is isotropic,
the susceptibility tensor is defined according to Eq. \ref{eq:K-isotropic}.
In this case, the magnetization $\mathbf{M}$ (Eqs. \ref{eq:M-KH} and \ref{eq:M-remanence}),
referred to the main coordinate system (Fig. \ref{fig:orientation-angles}a),
and the matrix $\mathbf{\Lambda}$ (Eq. \ref{eq:Lambda})
can be rewritten as follows:
\begin{equation}
\mathbf{M} = \mathbf{\Lambda} \left( \chi \, \mathbf{H}_{0} +
\mathbf{M}_{R} \right) \: ,
\label{eq:M-K-isotropic}
\end{equation}
and
\begin{equation}
\mathbf{\Lambda} = \mathbf{V}
\left( \mathbf{I} - \chi \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
\mathbf{V}^{\top} \: .
\label{eq:Lambda-K-isotropic}
\end{equation}
Despite the coordinate transformation represented by
matrix $\mathbf{V}$ (Eq. \ref{eq:A}),
this equation is in perfect agreement with those presented 
by \citet[Eqs. ~13--15]{guo2001}.
The first term, depending on the inducing field $\mathbf{H}_{0}$
(Eq. \ref{eq:H0}), 
represents the induced magnetization whereas the term depending on
$\mathbf{M}_{R}$ is the remanent magnetization.
Equation \ref{eq:M-K-isotropic} reveals that, as pointed out by
many authors
\citep[e.g.,][]{maxwell1873, dubois1896, stoner1945, clark1986, sttraton2007},
the induced magnetization opposes the inducing field 
if it is parallel to an ellipsoid axis, 
independently of the ellipsoid type. Otherwise, the
magnetization is not necessarily parallel to
the inducing field.
If we additionally consider that $\chi << 1$, the matrix 
$\mathbf{\Lambda}$ (Eq. \ref{eq:Lambda-K-isotropic})
approaches to the identity and the magnetization
$\mathbf{M}$ (Eq. \ref{eq:M-K-isotropic})
can be approximated by:
\begin{equation}
\breve{\mathbf{M}} = \chi \, \mathbf{H}_{0} +
\mathbf{M}_{R} \: ,
\label{eq:M-approx}
\end{equation}
which is the classical equation describing the resultant
magnetization in applied geophysics \citep[p. ~89]{blakely1996}.
Notice that, in this particular case, the induced magnetization
is parallel to the inducing field $\mathbf{H}_{0}$ (Eq. \ref{eq:H0}),
whether it is parallel to an ellipsoid axis or not.
Usually, Eq. \ref{eq:M-approx}
is considered a good approximation for $\chi \leq 0.1$ SI.
Although this value has been largely used in the literature,
there have been few empirical and/or theoretical investigations 
about it.

\subsubsection{Relationship between $\chi$ and the magnetization error}

In the case of isotropic susceptibility, the resultant magnetization
$\mathbf{M}$ (Eq. \ref{eq:M-K-isotropic}) may be determined by solving the
following linear system:
\begin{equation}
\mathbf{\Lambda}^{-1} \, \mathbf{M} = \chi \, \mathbf{H}_{0} +
\mathbf{M}_{R} \: ,
\label{eq:M-K-isotropic-inverse-Lambda}
\end{equation}
where, according to Eq. \ref{eq:Lambda-K-isotropic},
\begin{equation}
\mathbf{\Lambda}^{-1} = \mathbf{V}
\left( \mathbf{I} - \chi \, \tilde{\mathbf{N}}^{\dagger} \right)
\mathbf{V}^{\top} \: .
\label{eq:inverse-Lambda}
\end{equation}

Consider a perturbed matrix $\delta \mathbf{\Lambda}^{-1}$ given by
\begin{equation}
\delta \mathbf{\Lambda}^{-1} = \mathbf{\Lambda}^{-1} - \mathbf{I}
\label{eq:perturbed-inverse-Lambda}
\end{equation}
and, similarly, a perturbed magnetization vector $\delta \mathbf{M}$
given by
\begin{equation}
\delta \mathbf{M} = \mathbf{M} - \breve{\mathbf{M}} \: ,
\label{eq:perturbed-M}
\end{equation}
where $\mathbf{M}$ is the true magnetization obtained from Eq. 
\ref{eq:M-K-isotropic-inverse-Lambda} and $\breve{\mathbf{M}}$
is the approximated magnetization obtained from Eq. \ref{eq:M-approx}.
